$\bigtool$: JavaScript Specification Type Analyzer using Refinement

### 2021-08-15 paper/ase21/artifact/main.tex
Updated artifact pdf

\section{Getting Started Guide}
The artifact is open-source can be obtained by cloning the following git
repository:
\begin{lstlisting}
$ git clone --recurse-submodules \
  https://github.com/kaist-plrg/jstar.git
\end{lstlisting}
Please see \code{INSTALL.md} for the detailed guide of installation, how to use
this artifact.

@@

\subsection{Type Analysis}
JSTAR performs a type analysis with flow-sensitivity and type-sensitivity for
arguments.  Each function is split into multiple flow- and type-sensitive views,
and an abstract state stores mapping from views to corresponding abstract
environments.  To handle views separately, we use a worklist algorithm.  The
type analyzer consists of two sub-modules: an \textbf{Analysis Initializer} and
an \textbf{Abstract Transfer Function}.
\begin{itemize}
  \item \textbf{Analysis Initializer} defines the initial abstract state and the initial
    set of views for a worklist.
  \item \textbf{Abstract Transfer Function} gets a specific view from the worklist and
    updates the abstract environments of the next views based on the abstract
    semantics for each iteration.
\end{itemize}

@@

\begin{itemize}
  \item \textbf{Reference Checker} detects \textit{reference bugs} which occur
    when trying to access variables not yet defined (`UnknownVar`) or to
    redefine variables already defined (`DuplicatedVar`).
  \item \textbf{Arity Checker} detects \textit{arity bugs}. An arity bug occurs
    when the number of arguments does not match with the function arity
    (`MissingParam`).
  \item \textbf{Assertion Checker} detects \textit{assertion failures}. An
    assertion failure (`Assertion`) occurs when the condition of an assertion
    instruction is not true.
  \item \textbf{Operand Checker} detects \textit{ill-typed operand bugs}. An
    ill-typed operand bug occurs when the type of an operand does not conform to
    its corresponding parameter type.  It contains non-numeric operand bugs
    (`NoNumber`) and unchecked abrupt completion bugs (`Abrupt`).
\end{itemize}

>>>>

\section{Getting Started Guide}
The artifact is open-source can be obtained by cloning the following git
repository:
\begin{lstlisting}
$ git clone --recurse-submodules \
  https://github.com/kaist-plrg/jstar.git
\end{lstlisting}
Please see \code{INSTALL.md} for the detailed guide of installation, how to use
this artifact.  We also provide this artifact in Zenodo with a
DOI\footnote{https://doi.org/10.5281/zenodo.5084817}
and docker image as follows:
\begin{lstlisting}
$ docker run -it --rm jhnaldo/jstar
\end{lstlisting}

@@

\subsection{Type Analysis}
JSTAR performs a type analysis with flow-sensitivity and type-sensitivity for
arguments.  Each function is split into multiple flow- and type-sensitive views,
and an abstract state stores mapping from views to corresponding abstract
environments.  The type analyzer consists of two sub-modules: an
\textbf{Analysis Initializer} and an \textbf{Abstract Transfer Function}.
\begin{itemize}
  \item \textbf{Analysis Initializer} defines the initial abstract state and the initial
    set of views for a worklist.
  \item \textbf{Abstract Transfer Function} gets a specific view from the worklist and
    updates the abstract environments of the next views based on the abstract
    semantics for each iteration.
\end{itemize}

@@

\begin{itemize}
  \item \textbf{Reference Checker} detects \textit{reference bugs} which occur
    when trying to access variables not yet defined (`UnknownVar`) or to
    redefine variables already defined (`DuplicatedVar`).
  \item \textbf{Arity Checker} detects \textit{arity bugs}. An arity bug occurs
    when the number of arguments does not match with the function arity
    (`MissingParam`).
  \item \textbf{Assertion Checker} detects \textit{assertion failures}. An
    assertion failure (`Assertion`) occurs when the condition of an assertion
    instruction is not true.
  \item \textbf{Operand Checker} detects \textit{ill-typed operand bugs}. An
    ill-typed operand bug occurs when the type of an operand does not conform to
    its corresponding parameter type.
\end{itemize}
